Building Sustainable Software - The CSDMS Approach

### 2014-07-15 hutton_et_al_2014_wssspe.tex
Fixed spelling mistakes.

\begin{comment}
In order to realize the full power and benefits of component-based modeling, a
modeling framework like \csdms{} needs an efficient mechanism to convert as many
open-source models as possible to reusable plug-and-play components. Since this
necessarily requires some involvement from each model's developer (\emph{who,
likely, is not paid to do this}), this mechanism must require minimal effort
and the benifit to the developer should be clear.
In the first few years of the \csdms{} project, we worked directly with model
developers and conducted one-on-one interviews to hear their concerns and
complaints about early designs and other frameworks. In addition to being easy
to implement, the following requirements of a model wrapping procedure became
clear:
%Through working directly with model developers and listening to their concerns
%and complaints about early designs and other frameworks,
%the following requirements presented themselves:
\begin{itemize}

@@

\csdms{} has built an online model repository that not only contains model
source code but also documents the submitted code as model metadata, runs
basic smoke-tests of the models, (optionally) maintains the source code in a
\csdms{}-hosted version control system, and provides easy downloads of the
original source. The repository now contains over 200 models and tools (over
4M lines of code) and has recieved over 13k model downloads.

>>>>

\begin{comment}
In order to realize the full power and benefits of component-based modeling, a
modeling framework like \csdms{} needs an efficient mechanism to convert as many
open-source models as possible to reusable plug-and-play components. Since this
necessarily requires some involvement from each model's developer (\emph{who,
likely, is not paid to do this}), this mechanism must require minimal effort
and the benefit to the developer should be clear.
In the first few years of the \csdms{} project, we worked directly with model
developers and conducted one-on-one interviews to hear their concerns and
complaints about early designs and other frameworks. In addition to being easy
to implement, the following requirements of a model wrapping procedure became
clear:
%Through working directly with model developers and listening to their concerns
%and complaints about early designs and other frameworks,
%the following requirements presented themselves:
\begin{itemize}

@@

\csdms{} has built an online model repository that not only contains model
source code but also documents the submitted code as model metadata, runs
basic smoke-tests of the models, (optionally) maintains the source code in a
\csdms{}-hosted version control system, and provides easy downloads of the
original source. The repository now contains over 200 models and tools (over
4M lines of code) and has received over 13k model downloads.
